---
title: "CLT_WUP"
author: "Marta Marriott"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```

```{r}
numb=2
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k2 = x.avg

p <- ggplot(my1000, aes(x=k2)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k2)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k2),' sd = ',sd(my1000$k2)))

```
## We expect the sample mean to be close to population and the standev to get smaller by the ratio of one to the sample size. In this case 1/sqrt(2)

### There are 3 peaks in the density plot. You pick two people you can get MM,MF.FM,or FF. these are all equally likey so the little peak on left is all the FF's while the little peak on the right is all the MM's so the big one in the middle is both the MF and FM in the same bag so-to-speak.  

```{r}
numb = 4
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k4 = x.avg


p <- ggplot(my1000, aes(x=k4),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k4)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 4") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k4),' sd = ',sd(my1000$k4)))

```

### In this case the stdev was cut in half because the sample size was four. This is what the central limit theorem says. There are also 5 peaks. They go from FFFF,to FFFM, to FFMM to FMMM and finally MMMM.

```{r}
numb=9
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k9 = x.avg

p <- ggplot(my1000, aes(x=k9)) + 
  geom_density() 

# Add mean line
  geom_vline(aes(xintercept=mean(k9)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 9") +
  xlab("temperature") + ylab("density")
  
print(paste('mean = ', mean(my1000$k9),' sd = ',sd(my1000$k9)))

```

The previous graph showed the mean is closer to 50, and the standard deviation is decreasing in accordance to the Central Limit Theory. This was expected as standard deviation for the sample was 41.83, which when divided by the square root of 9 gives a standard deviation of 13.93 or a standard deviation of 14.


```{r}
numb=16
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k16 = x.avg

p <- ggplot(my1000, aes(x=k16)) + 
  geom_density() 

# Add mean line
  geom_vline(aes(xintercept=mean(k16)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 16") +
  xlab("temperature") + ylab("density")

  print(paste('mean = ', mean(my1000$k16),' sd = ',sd(my1000$k16)))

```

The graph is beginning to look more symmetrical as the sample size has increased to 16, which can result in a higher frequency of discrepancies of opinion. The standard deviation is also decreasing as we are dividing 16 by the square root of 4, which gives a result of 4 for this sample size.

```{r}
numb=25
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k25 = x.avg

p <- ggplot(my1000, aes(x=k25)) + 
  geom_density() 

# Add mean line
  geom_vline(aes(xintercept=mean(k25)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 25") +
  xlab("temperature") + ylab("density")

  print(paste('mean = ', mean(my1000$k25),' sd = ',sd(my1000$k25)))

```

The graph is looking increasingly more symmetrical, as the sample size has increased to 25 which increases the frequency for discrepancies of opinion. The standard deviation had decreased once again as we are now dividing the sample size of 25 by the square root of 5, which gives a result of 5 for this sample size.

```{r}
numb=36
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k36 = x.avg

p <- ggplot(my1000, aes(x=k36)) + 
  geom_density() 

# Add mean line
  geom_vline(aes(xintercept=mean(k36)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 36") +
  xlab("temperature") + ylab("density")

  print(paste('mean = ', mean(my1000$k36),' sd = ',sd(my1000$k36)))

```

The graph has increased symmetrically once again, as we used a sample size of 36, which increases the frequency of discrepancy of opinion. The standard deviation has also decreased as we are dividing our sample size of 36 by the square root of 6 which gives a result of 6 for this sample size. This graph, along with the previous graphs demonstrates the Central Limit Theory by the standard deviation decreasing as we increase the sample size.







